\section{Additional Qualifications}

% New bullet point for the next sections
\renewcommand{\labelitemi}{o}
\subsection{\textbf{\textcolor{red}{Patents}}}
	\cvline{2022}
    {"Visual positioning system for multi-rotor UAVs for high-precision autonomous landing";\textbf{Sevostyanov Ilya Evgenievich (RU),Devitt Dmitry Vladimirovich (RU),Shashkina Ksenia Mikhailovna (RU),Shaghaei Ehsan (IR) ;} "The program provides accurate landing of the UAV in offline mode. The system does not depend on the time of day and weather conditions. The system uses cameras and special markings in the form of LED markers to accurately determine the location and direction of the landing site at a great distance."  \href{https://new.fips.ru/registers-doc-view/fips_servlet?DB=EVM&DocNumber=2022610258}{\textcolor{blue}{RUSSIAN FEDERAL SERVICE
ON INTELLECTUAL PROPERTY 2022610258} }}

\subsection{\textbf{\textcolor{red}{Publications}}}
	
	% \cvline{2022[Pending]}{"Improved Design and Realization of Pulsed BPSK, QPSK, Barker Encoded, CW and Chirp Signal Generation in LabVIEW PXI 5644R";\textbf{Zarrar Haider, Ehsan Shaghaei, Furqan Haider, Malik Muhammad Zohaib};  2022 International Conference on Signal and Image Processing }
    \cvline{2022[Pending]}
    {"CASE STUDY: ANPR utilized for Smart Parking";\textbf{E. Shaghaei, G.Imbugwa, M.Pezer, M.Mazzara;} CSCT2022. Presented on December 11,2022. \href{https://drive.google.com/file/d/1HQON2v-FcR6aVfwKHJz9oor0xCwBEwab/view?usp=sharing}{\textcolor{blue}{submission copy}}}
	\cvline{2022}{"Breast Cancer Detection and Classification using Machine Learning with Artificial Neural Networks in LabVIEW Vision ";\textbf{Zarrar Haider, Ehsan Shaghaei, Furqan Haider, Manuel Mazzara};  \href{https://www.researchgate.net/publication/362538010_Breast_Cancer_Detection_and_Classification_using_Machine_Learning_with_Artificial_Neural_Networks_in_LabVIEW_Vision}{\textcolor{blue}{DRAFT}} }
    
	\cvline{2022}{"Investigation of ACS image stabilization of on-board optoelectronic guidance and tracking devices.";\textbf{Burdinov K.A., Shashkina K.M., Shaghaei E.};   Advanced Engineering Research. \href{https://doi.org/10.23947/2687-1653-2022-22-2-150-160}{\textcolor{blue}{doi: 10.23947/2687-1653-2022-22-2-150-160}}}
    

	\cvline{2021}{"Mathematical Modeling and Control System Design of Flapping Wing Unmanned Air Vehicle"\textbf{ Z. Haider, M. M. Zohaib, F. Haider and E. Shaghaei } 2021 4th International Conference on Robotics, Control and Automation Engineering (RCAE), 2021, pp. 224-228, \href{https://ieeexplore.ieee.org/document/9638883}{\textcolor{blue}{doi: 10.1109/RCAE53607.2021.9638883.}}}
	

	\cvline{2017}{GLPS Positioning System;\textbf{Shaghaei,Ehsan;}\textit{14th CRRS National Mathematics Conference (CRRS 2017):} My First Experience in as an scholar and a school student. Here developed naive yet interesting mathematical model for increasing accuracy of GPS. My method purposed using accelerator and shaft-encoder data to append a local positioning method to L1 distance GPS in order to solve challenge of high latency of GPS. Apparently, I didn't know about L2  and higher frequency methods by the time :-D }
\newpage
\subsection{\textbf{\textcolor{red}{Workshops and Cerificates}}}

\cvline{}{
        \begin{itemize}
            \item Practical Machine Learning and Deep Learning (100/100)
            \item Advanced Linux Understanding and Development (100/100)
            \item \href{https://drive.google.com/file/d/1CNFCEVaNYJb2H13lgbo4JMemKjn8jbhF/view?usp=sharing}{\textcolor{blue}{Intro. to ARM processors and STM32 microcontrollers (5/5)}}
            \item Digital Signal Processing (100/100)
            \item High-Performance Techniques for modern Cpp (volunteer)
            \item \href{https://drive.google.com/file/d/1yvqTUIXnw2QqXI24fEhVDrQA3yKe5KuA/view?usp=sharing}{\textcolor{blue}{Android Mobile Development  (90/100)}}
        \end{itemize}
        }

\subsection{\textbf{\textcolor{red}{Accomplishments}}}

\cventry{2021}
{\textbf{3th Place of Huawei Challenge Hackaton 2021}}
{Innopolis, Russia}
{}
{}
{
"IU team V2"team ; Optimizing firewall rule matching algorithm performance
Solved the challenge for providing a solution for firewall rule matching and routing. 
        Increased the benchmark of the rule matching task by  because of using the efficient data structure 'Trie' for storing the firewall rules and using compiler techniques to optimise code latency. 
 }

\cventry{2021}
{\textbf{Argo-Code Unamanned Tech Hackaton }}
{Innopolis, Russia}
{}
{}
{
" self-driving IU" team ; Developing an autonomous system for tracking obstacles and path planning. 
} 
 
\cventry{2019}
{\textbf{3rd Place of InnoRoboHack }}
{Innopolis, Russia}
{}
{}
{
36,000 Rub(600 USD) Prize.
Innosteros Team; Developed a Computer Vision based navigation to control a simulation of a lunar explorer robot 
}
 
\cventry{2014}
{\textbf{1st Place of RoboCup 2014}}
{Joao Pessoa, Brazil}
{\newline PCB Designer, Frimware Developer}
{}
{
\href{http://www.robocup2014.org/?page_id=3318}{\textcolor{blue}{R2T Team}}, Junior Rescue B League; \href{https://drive.google.com/file/d/1r-OCgC7kt6sOVfw2KTvrFq5kaBQ-nFiU/view?usp=sharing}{\textcolor{blue}{SUPER-TEAM advance award}}}


 
\cventry{2014}
{\textbf{1st Place of IranOpen 2014 (National Robocup)}}
{Tehran,Iran}
{\newline PCB Designer, Frimware Developer}
{}
{
	R2T Team, Junior Rescue A League, \href{https://drive.google.com/file/d/1SVeY8KieeonJo1rX8eTNVhbd5ya61Gct/view?usp=sharing}{\textcolor{blue}{First Place Award}}
}

\cventry{2015}
{\textbf{3rd Place National Olympiad in Informatics }}
{Mashhad,Iran}
{}
{}
{	
}


\cventry{2018}
{\textbf{"Konkoor" National University Entrance Examination}}
{Tehran,Iran}
{}
{}
{
Among top 0.02\% qualified applicants for full-fund education at AmirKabir University of Technology between 340000 Applicants
}


\cventry{2016}
{\textbf{2rd place of World Skills Olympiad (Regional Stage)}}
{Tehran,Iran}
{}
{}
{
  at-Work Robot : *The Youngest Participant.
}

\cventry{2015}
{\textbf{1st Place of Khwarizmi Youth Award }}
{Tehran,Iran}
{}
{}
{
    Developed a Smart Chess board which tracks the players moves.
}



\cventry{2014}
{\textbf{3rd Place of Arithland Mathematics Olympiad (National) }}
{Mashhad,Iran}
{Ferdowsi University of Mashhad}
{\href{https://drive.google.com/file/d/1m13vduTQe1rsCELSdiigq0-Qgep3Pecu/view?usp=sharing}{\textcolor{blue}{Award}}}
{}

\cventry{2014}
{\textbf{NODET High Schools Entrance Exam}}
{Mashhad,Iran}
{}
{}
{
Among top 1\% qualified applicants for full-fund education at National Organization for Development of Exceptional Talents(NODET) for High School and college with scholarship from National Elites Foundation
}

\cventry{2013}
{\textbf{1st Place of Warrior-Bot 126th Cup }}
{Mashhad,Iran}
{}
{}
{
   Ahuratus team. Developed a warrior robot with hydraulics lifter jack.
}

% \cventry{2013}
% {\textbf{1st Place of “Dahe-e-Fajr” Art Award }}
% {Mashhad,Iran}
% {}
% {}
% {
% 	Play-reading; School theater team
% }
