\section{Experience}


\subsection{\textbf{Work}}

\cventry{2021 - Now}
        {Part-Time Embedded Engineer}
        {Autonomous Vehicles Technology}
        {Innopolis, Russia}
        {
        Developed Real-Time Nodes which was utilized in a distributed system for controlling UAVs. Automated the pipeline of testing and build the firmwares.
        } 
        {
        \begin{itemize}
            \item Embedded C, UART, SPI, I2C, CAN
            \item gcc-arm-none-eabi
            \item UAVCAN-v0
            \item gh-actions
            \item doxygen
        \end{itemize}
        }
\cventry{2021}
        {Cpp Developer}
        {Huawei}
        {Kazan, Russia}
        {
            Solved the challenge for providing a solution for firewall rule matching and routing. 
            Increased the benchmark of the rule matching task by 60\% because of using the efficient data structure 'Trie' for storing the firewall rules. 
        }
        {}
\cventry{2020 - Now}
        {Part-Time Embedded Engineer}
        {Laboratory of Quantum optics and  computing  in  Kazan Scientific Center}
        {Kazan, Russia}
        {
        Developing high-speed driver for Laboratory Hardware, developed an open-source \href{https://pypi.org/project/holoeye-embedded/}{\color{blue}python package} for interfacing Spital-Light-Modulator device.    
        } 
        {
        \begin{itemize}
            \item Embedded C
            \item RNDIS
            \item SSH
            \item twin
            \item sphinx
        \end{itemize}
        }



\subsection{\textbf{Internships}}


\cventry{05/2022 - 07/2022}
                {Data Engineer Intern}
                {Schwarzthal Tech}
                {London, UK}
                {Crawling the data of legal entities in different countries, Improved the crawling pip-line performance simply by finding a shortcut to \textbf{bypass submitting the request form,credentials and captcha}, hence a more efficient pipeline which resulted in \textbf{less bill for AWS}.  } 
                {
                \begin{itemize}
                    \item Scrappy
                    \item Spiders
                    \item ASP.net 
                \end{itemize}
                }
        
\cventry{02/2022 - *}
        {Data Engineer Intern}
        {McKinsey \& Company}
        {Moscow, Russia}
        {Passed the exams and test tasks on SQL, python, pandas and scikit learn.
        Learnt about different case studies and EDA techniques.
        } 
        {
        \textit{The case was freezed because of the Moscow office closure due to start of Special Operation by Russia.}
        }
        

\cventry{05/2021 - 07/2021}
        {Embedded Engineer Intern}
        {Innopolis Unviersity}
        {Innopolis, Russia}
        {
        Developed frimware for Real-Time Nodes which was utilized in a distributed system for controling UAVs. Check my \href{https://drive.google.com/file/d/1Msw5tk7niDSDpVlNeaLCsUIQxlgREYcV/view?usp=sharing}{\color{blue} recommendation letter} on this internship.
        }
        {
        \begin{itemize}
            \item FreeRTOS
            \item UAVCAN v0
            \item gcc-arm-none-eabi
        \end{itemize}
        }


\cventry{06/2018 - 09/2018}
        {Software Engineer Intern}
        {Siemens Research}
        {Mashhad, Iran}
        {Development of OTA-frimware upgrade system for Automation industry} 
        {
        \begin{itemize}
            \item sockets('sys/socket')
            \item UART
            \item TIA portal 
        \end{itemize}
        }

        